Eurovision Song Contest: semifinal 1, 2009

### 2022-07-14 inst/eurovision.Rmd
improvements to graph

```{r,maximi,cache=TRUE}
lam <- seq(from=0.5,to=2,len=10)
L <- sapply(lam,o)
```

```{r,plotmaximi}
plot(lam,L-max(L),type="b",pch=16)
```

>>>>

```{r,maximi,cache=TRUE}
lam <- seq(from=0.6,to=2,len=20)
L <- sapply(lam,o)
```

```{r,plotmaximi}
plot(lam,L-max(L),type="b",pch=16)
abline(h=c(0,-2))
abline(v=1)
```
